# Drug Trials 
A new drug has a 70% success rate.

### Load libraries
library(ggplot2)

### Experiments
Take a random sample of 10 patients.

**What is the probability that at least 8 are successfully treated?**
```{r}
pbinom(8, size = 10, prob = 0.7, lower.tail = FALSE)
```

**Median number of successful treatments**
For looking at the median we can use `qbinom` to look at the distribution for a specific quartile, in this case the median so .50.
```{r}
qbinom(0.5, size = 10, prob = 0.7)
```

**Binomial probabilities for 0 to 10 successes**
```{r}
successes <- 0:10
probabilities <- dbinom(successes, size = 10, prob = 0.7)

plot(successes,
     probabilities,
     type = "h",
     lwd = 4,
     las = 1,
     xlab = "Number of Patients with Successes",
     ylab = "Probability")

# fancier with ggplot
df_success <- data.frame(Successes = successes, Probability = probabilities)

# plot probability mass function
ggplot(df_success, aes(x = Successes, y = Probability)) +
  geom_bar(stat = "identity", fill = "seagreen", color = "black") +
  theme_minimal() +
  labs(title = "Probability Mass Function of Drug Successes",
       x = "Number of Successful Treatments",
       y = "Probability")
```


