# Olympic Archery Scores
In Olympic archery, competitors aim to hit the bullseye for the highest score. The total score over 10 rounds for elite
archers follows a normal distribution with:
    Mean score = 85
    Standard deviation = 5

**What is the probability of an archer scoring below 80?**
```{r}
pnorm(80, mean = 85, sd = 5)
```

**What is the minimum score someone must receive to be in the top 10%?**
This would mean they are in the 90th percentile.
```{r}
qnorm(0.90, mean = 85, sd = 5)
```

**Simulate 1000 Olympic archers**
```{r}
# set seed for reproducibility
set.seed(42)
archery_scores <- rnorm(1000, mean = 85, sd = 5)

library(ggplot2)
df_scores <- data.frame(Score = archery_scores)

ggplot(df_scores, aes(x = Score)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "blue", color = "black") +
  stat_function(fun = dnorm, args = list(mean = 85, sd = 5), color = "red", size = 1) +
  theme_minimal() +
  labs(title = "Olympic Archery Score Distribution", x = "Score", y = "Density")
```
