# Quality Control in Manufacturing
A factory produces light bulbs, and the probability that a randomly selected bulb is defective is 5%. 

### Load libraries
library(ggplot2)

## Experiments
For the purposes of the experiment we select 20 bulbs.

**What is the probability of finding exactly 3 defective bulbs?**
Want to use `dbinom` here to get the probability "density" of a particular value.
```{r}
exactly3 <- dbinom(3, size = 20, prob = 0.05)
exactly3
```

**What is the probability of finding at most 3 defective bulbs?**
This is essentially everything up to 3. The `pbinom` function gives us the distribution probability.
```{r}
at_most3 <- pbinom(3, size = 20, prob = 0.05, lower.tail = TRUE)
at_most3
```

**Simulate 100 trials of inspecting 20 bulbs and visualize the distribution.**
```{r}
# simulate 100 trials of 20 inspections
set.seed(29)  # for reproducibility
random_sample <- rbinom(100, size = 20, prob = 0.05)

# ugly strip chart
stripchart(random_sample,
           method = "stack",
           las = 1,
           pch = 16,
           cex = 0.75,
           ylim = c(0, 10),
           xlim = c(0, 5),
           xlab = "Number of Defective Bulbs",
           ylab = "Frequency",
           main = "Defective Bulbs in a Random Sample of 20")

# convert to dataframe for plotting
df <- data.frame(Defective_Bulbs = random_sample)
df

# plot histogram of simulated defective bulbs
ggplot(df, aes(x = Defective_Bulbs)) +
  geom_bar(fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Defective Bulbs in 100 Trials",
       x = "Number of Defective Bulbs",
       y = "Frequency")

print(paste("Probability of exactly 3 defective bulbs:", exactly3))
print(paste("Probability of at most 3 defective bulbs:", at_most3))
```

**Can we use the Central Limit Theorem to make the binomial distribution look more like a normal distribution?**
```{r}
set.seed(29)  # for reproducibility
random_sample <- rbinom(1000, size = 1000, prob = 0.05)

df <- data.frame(Defective_Bulbs = random_sample)

# plot histogram of simulated defective bulbs
ggplot(df, aes(x = Defective_Bulbs)) +
  geom_bar(fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Defective Bulbs in 100 Trials",
       x = "Number of Defective Bulbs",
       y = "Frequency")
```