# Rollercoaster Speeds
Roller coaster speeds follow a normal distribution due to engineering constraints and safety standards. 
For a famous amusement park, the speeds of rides are normally distributed with:
    Mean speed = 90 km/h
    Standard deviation = 15 km/h

**Simulate rollercoaster speeds for 1000 rollercoasters**
```{r}
# set seed and generate 1000 rollercoaster speeds
set.seed(42)
coaster_speeds <- rnorm(1000, mean = 90, sd = 15)

# put the data into a data frame
df_speeds <- data.frame(Speed = coaster_speeds)

# create a histogram
ggplot(df_speeds, aes(x = Speed)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "orange", color = "black") +
  stat_function(fun = dnorm, args = list(mean = 90, sd = 15), color = "red", size = 1) +
  theme_minimal() +
  labs(title = "Roller Coaster Speed Distribution", x = "Speed (km/h)", y = "Density")
```

**What's the probability of the rollercoaster going over 100km/h?**
```{r}
pnorm(110, mean = 90, sd = 15, lower.tail = FALSE)
```

**What's the speed of the slowest 5% of rollercoasters?**
```{r}
qnorm(0.05, mean = 90, sd = 15)
```